Efficient Calculation of Improved Simultaneous Testing Bands for QQplots with \proglang{R} Package \pkg{qqconf}

### 2021-04-25 article/manuscript.Rnw
added code to set min and max on ci addition

A number of methods have been created towards this end. Naively, one could put pointwise testing bands onto QQplots, which conduct $\alpha$ level tests on each order statistic of the sample. This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified null distribution. To appropriately deal with this multiple testing problem, the Komolgorov-Smirnov (KS) statistic is commonly used to create joint testing bands \citep{kolmogoroff1941confidence, smirnov1944approximate}. While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power}. A more promising approach, originally introduced by Berk and Jones and later developed by Gontscharuk et al., conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2016goodness}. Because this test, which will be referred to as equal local levels (ELL), conducts an $\eta$ level test on each order statistic, it is agnostic to any alternative distribution. This makes ELL a sensible choice for a standard test to use in creating testing bands on QQplots, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.

>>>>

A number of methods have been created towards this end. Naively, one could put pointwise testing bands onto QQplots, which conduct $\alpha$ level tests on each order statistic of the sample. This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified null distribution. To appropriately deal with this multiple testing problem, the Komolgorov-Smirnov (KS) statistic is commonly used to create joint testing bands \citep{kolmogoroff1941confidence, smirnov1944approximate}. While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power}. A more promising approach, originally introduced by Berk and Jones and later developed by Gontscharuk et al., conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2015intermediates, gontscharuk2016goodness}. Because this test, which will be referred to as equal local levels (ELL), conducts an $\eta$ level test on each order statistic, it is agnostic to any alternative distribution. This makes ELL a sensible choice for a standard test to use in creating testing bands on QQplots, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
